Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-22 conclusions.tex
Split compound sentence
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1138 ccdd05d5-56c1-461a-bf98-85f6876523b4

The detection algorithm we described has no intrinsic latency.  However, there are
fundamental and practical latencies associated with the analysis and detection
procedure. For example, the \LIGO{} data acquisition records science data in 1/16~s
blocks~\citep{Bork2001}. Data must also be aggregated from all of the \GW\
observatories using global computer networks capable of high bandwidth but perhaps only
modest latency.  This could introduce a latency of $\sim$100~ms.  Lastly, unless a
real-time infrastructure is adopted post data acquisition, it is likely that there will be 
an inherent latency introduced by the software architecture itself.  We have shown 
prototype implementation of \lloid{} using the open source signal processing platform
\gstreamer. Significant work would have to be done in order to
improve upon the latency of our implementation, including tighter integration between
data acquisition and analysis. This could be considered for third-generation detector
design.
Also possible for third-generation instruments, the \lloid{} method could
provide the input for a dynamic tuning of detector response via the signal
recycling mirror to match the frequency of maximum sensitivity to the
instantaneous frequency of the \GW{} waveform; this challenging technique has
the potential for vast gains in \SNR{} and timing accuracy
\citep{PhysRevD.47.2184}.

>>>>

The detection algorithm we described has no intrinsic latency.  However, there are
fundamental and practical latencies associated with the analysis and detection
procedure. For example, the \LIGO{} data acquisition records science data in 1/16~s
blocks~\citep{Bork2001}. Data must also be aggregated from all of the \GW\
observatories using global computer networks capable of high bandwidth but perhaps only
modest latency.  This could introduce a latency of $\sim$100~ms.  Lastly, unless a
real-time infrastructure is adopted post data acquisition, it is likely that there will be 
an inherent latency introduced by the software architecture itself.  We have shown 
prototype implementation of \lloid{} using the open source signal processing platform
\gstreamer. Significant work would have to be done in order to
improve upon the latency of our implementation, including tighter integration between
data acquisition and analysis. This could be considered for third-generation detector
design.
Also possible for third-generation instruments, the \lloid{} method could
provide the input for a dynamic tuning of detector response via the signal
recycling mirror to match the frequency of maximum sensitivity to the
instantaneous frequency of the \GW{} waveform.  This is a challenging technique, but
it has the potential for vast gains in \SNR{} and timing accuracy
\citep{PhysRevD.47.2184}.
